### 2019-05-14 README.Rmd
fixed typos in paper and readme
binder integration 2

[![Travis-CI Build Status](https://travis-ci.org/danielpearson90/vmacfeaturesearch.svg?branch=master)](https://travis-ci.org/danielpearson90/vmacfeaturesearch)

@@

> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

>>>>

[![Travis-CI Build Status](https://travis-ci.org/danielpearson90/vmacfeaturesearch.svg?branch=master)](https://travis-ci.org/danielpearson90/vmacfeaturesearch) [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/danielpearson90/vmacfeaturesearch/master/?urlpath=rstudio)

@@

> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (2019). _`r Title`_. PsyArXiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.31234/osf.io/db9hg>
